SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-25 scipy-1.0/paper.tex
Describe the stats.distributions framework.

\subsection*{Statistical distributions}

We now provide the cumulative distribution function (using the Fortran code by
Alan Genz) of the multivariate normal distribution, \\\texttt{scipy.stats.multivariate\_normal},
via the newly associated \texttt{logcdf} and \texttt{cdf} methods. Other key recent distributions 
added to \texttt{scipy.stats} include the histogram-based
distribution in \texttt{scipy.stats.rv\_histogram} and the multinomial
distribution in \texttt{scipy.stats.multinomial} (used, for example, in natural
language processing\cite{Griffiths5228}). \texttt{multinomial} is the first and so 
far the only multivariate discrete distribution available in SciPy.

From a design standpoint, many functions in \texttt{scipy.stats} now support
a \texttt{nan\_policy} keyword to allow user-level control over the algorithmic
decision to propagate, omit, or raise an error in the case that \texttt{NaN}
values are encountered. Much of the functionality offered by
\texttt{scipy.stats} for drawing random variates now accepts a
\texttt{random\_state} parameter, which is either a \texttt{numpy.random.RandomState}
object or an integer used to generate such an object, to provide fine-grained
user-level control over the random state of a workflow.

>>>>

\subsection*{Statistical distributions}
The \texttt{scipy.stats} module provides a framework to implement probability
distributions.  Given an expression for a probability distribution function (pdf),
the framework will calculate moments, cumulative distribution function (cdf),
differential entropy, and more. Those properties are calculated based on
generic code, e.g., numerical integration of the pdf to obtain the cdf. In cases
where that generic code does not provide sufficient accuracy, it is replaced
by an implemented specific to the distribution.
The distributions framework also allows the user to draw random
variates from the distribution. Drawing random variates now accepts a \texttt{random\_state}
parameter, which is either a \texttt{numpy.random.RandomState} object or an
integer used to generate such an object, to provide fine-grained user-level
control over the random state of a workflow.
Currently about 80 continuous univariate distributions, 12 discrete univariate
distributions and 10 multivariate distributions are implemented.
Key recent distributions added to \texttt{scipy.stats} include the histogram-based
distribution in \texttt{scipy.stats.rv\_histogram} and the multinomial
distribution in \texttt{scipy.stats.multinomial} (used, for example, in natural
language processing\cite{Griffiths5228}). \texttt{multinomial} is the first and so 
far the only multivariate discrete distribution available in SciPy.
